### 2022-09-12 Bloods_LMM.Rmd
Electrolytes Plots and LMM for Percentage Change

```

#Sodium
```{r}
NaLMM <- lmer(cal_Na ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = main_df2)
summary(NaLMM)
pairwise_NaLMM <- emmeans(NaLMM, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
pairwise_NaLMM
```

@@

#Potassium
```{r}
KLMM <- lmer(cal_K ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = main_df2)
summary(KLMM)
pairwise_KLMM <- emmeans(KLMM, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
pairwise_KLMM
```

@@

#Chlorine

@@

>>>>

```
#Total Change
##Sodium
```{r}
NaLMM <- lmer(cal_Na ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = main_df2)
summary(NaLMM)
pairwise_NaLMM <- emmeans(NaLMM, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
pairwise_NaLMM
```

@@

##Potassium
```{r}
KLMM <- lmer(cal_K ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = main_df2)
summary(KLMM)
pairwise_KLMM <- emmeans(KLMM, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
pairwise_KLMM
```

@@

##Chlorine

@@

#Percentage Change
##Sodium
```{r}
NaLMM_PCHANGE <- lmer(P_CHANGE ~ Time_Point + BFR + speed + Time_Point*BFR + Time_Point*speed + (1|Participant), data = sodium_PCHANGE_CL)
summary(NaLMM_PCHANGE)
pairwise_NaLMM_PCHANGE <- emmeans(NaLMM_PCHANGE, pairwise ~ Time_Point + BFR + speed + Time_Point*BFR + Time_Point*speed, adjust="holm")
pairwise_NaLMM_PCHANGE
```

```{r}
tab_model(NaLMM_PCHANGE)
```

##Potassium - Time points taken out currently
```{r}
KLMM_PCHANGE <- lmer(P_CHANGE ~ BFR + Speed + Speed*BFR + (1|Participant), data = potassium_PCHANGE_CL)
summary(KLMM_PCHANGE)
pairwise_KLMM_PCHANGE <- emmeans(KLMM_PCHANGE, pairwise ~ BFR + Speed + Speed*BFR, adjust="holm")
pairwise_KLMM_PCHANGE
```

```{r}
tab_model(KLMM_PCHANGE)
```

##Chloride
```{r}
ClLMM_PCHANGE <- lmer(P_CHANGE ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = chloride_PCHANGE_CL)
summary(ClLMM_PCHANGE)
pairwise_ClLMM_PCHANGE <- emmeans(ClLMM_PCHANGE, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
pairwise_ClLMM_PCHANGE
```

```{r}
tab_model(ClLMM_PCHANGE)
```

### 2022-09-12 Draft Plots.Rmd
Electrolytes Plots and LMM for Percentage Change

@@

##Electrolyte Grouping
```{r}
ELECTROLYTE_Grouping <- ggarrange(Na_PLOT_2,Cl_PLOT_2,K_PLOT_2,labels=c("A", "B", "C"), ncol=3, nrow=1, common.legend = TRUE, legend = "bottom")

>>>>

##Sodium
```{r}
sodium_PCHANGE_CL_SUM$Session_f = factor(sodium_PCHANGE_CL_SUM$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
 Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
 names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")

sodium_PCHANGE_CL_SUM$Time_Point_f = factor(sodium_PCHANGE_CL_SUM$Time_Point, levels=c("2", "3"))
Time_Point.labs<- c("Post-Exercise Finger", "Post-Exercise Toe")
names(Time_Point.labs)<-c("2", "3")

Sodium_PLOT_PCHANGE <- ggplot(sodium_PCHANGE_CL_SUM, aes(x = Time_Point_f, y= P_CHANGE))+
            geom_errorbar(aes(ymin = P_CHANGE-se, ymax =P_CHANGE+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(21, 16,22, 15))+
            theme_classic()+
            ggtitle("Sodium")+
            theme(plot.title = element_text(hjust = 0.5))+
            theme(legend.position="", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            scale_y_continuous(name = "Percentage Change \n",breaks = c(-10,0,10,20,30,40,50), limits = c(-10,50))+
            scale_x_discrete(breaks=c("2", "3"),
              labels=c("Post-Exercise Finger", "Post-Exercise Toe"))+

Sodium_PLOT_PCHANGE

##Potassium
```{r}
potassium_PCHANGE_CL_SUM$Session_f = factor(potassium_PCHANGE_CL_SUM$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
 Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
 names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")

potassium_PCHANGE_CL_SUM$Time_Point_f = factor(potassium_PCHANGE_CL_SUM$Time_Point, levels=c("2", "3"))
Time_Point.labs<- c("Post-Exercise Finger", "Post-Exercise Toe")
names(Time_Point.labs)<-c("2", "3")

potassium_PLOT_PCHANGE <- ggplot(potassium_PCHANGE_CL_SUM, aes(x = Time_Point_f, y= P_CHANGE))+
            geom_errorbar(aes(ymin = P_CHANGE-se, ymax =P_CHANGE+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(21, 16,22, 15))+
            theme_classic()+
            ggtitle("Potassium")+
            theme(plot.title = element_text(hjust = 0.5))+
            theme(legend.position="", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            scale_y_continuous(name = "Percentage Change \n",breaks = c(-10,0,10,20,30,40,50), limits = c(-10,50))+
            scale_x_discrete(breaks=c("2", "3"),
              labels=c("Post-Exercise Finger", "Post-Exercise Toe"))+

potassium_PLOT_PCHANGE

##Chloride
```{r}
chloride_PCHANGE_CL_SUM$Session_f = factor(chloride_PCHANGE_CL_SUM$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
 Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
 names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")

chloride_PCHANGE_CL_SUM$Time_Point_f = factor(chloride_PCHANGE_CL_SUM$Time_Point, levels=c("2", "3"))
Time_Point.labs<- c("Post-Exercise Finger", "Post-Exercise Toe")
names(Time_Point.labs)<-c("2", "3")

chloride_PLOT_PCHANGE <- ggplot(chloride_PCHANGE_CL_SUM, aes(x = Time_Point_f, y= P_CHANGE))+
            geom_errorbar(aes(ymin = P_CHANGE-se, ymax =P_CHANGE+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(21, 16,22, 15))+
            theme_classic()+
            ggtitle("Potassium")+
            theme(plot.title = element_text(hjust = 0.5))+
            theme(legend.position="", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            scale_y_continuous(name = "Percentage Change \n",breaks = c(-20,-10,0,10,20,30,40,50), limits = c(-20,50))+
            scale_x_discrete(breaks=c("2", "3"),
              labels=c("Post-Exercise Finger", "Post-Exercise Toe"))+

chloride_PLOT_PCHANGE

@@

#Electrolyte Grouping
```{r}
ELECTROLYTE_Grouping <- ggarrange(Na_PLOT_2,Cl_PLOT_2,K_PLOT_2,labels=c("A", "B", "C"), ncol=3, nrow=1, common.legend = TRUE, legend = "bottom")
